resistanceModelNotesAndy

### 2016-03-09 paper1_results_figs.Rmd
figures

@@

>>>>

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mixA_not20pc_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 / ggSubset$gen_cP0.25seq <= 0.2, 1, 0 )

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_diff))+

             facet_grid( ~ mixA_not20pc_better_seq0.25, labeller=as_labeller( c('0'='adaptive mix\nresistance >20% slower','1'='adaptive mix\nresistance <20% slower'))) +

             theme_bw() +
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points abs_diff
             geom_smooth(data=df_same, method = "lm", se = FALSE) 
           )

### 2016-03-09 paper1_results_figs_slimmed.Rmd
figures

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.
1. Effectiveness of the insecticides is the one input that can change the average relative positioning of the strategies a) sequential and b) adaptive mixture. Below an effectiveness of ~0.55 to 0.6 sequential takes longer to reach the resistance threshold, and above this the adaptive mixture takes longer. 
1. Exposure and effectiveness come out as the most important effect on the difference between the sequential and adpative mixture strategies.
1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.

@@

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='red')
           )       
```
Grey triangles are those runs in which resistance reached the threshold at the same time in the two strategies (and are repeated in both panels). The grey line is a linear model through these same points.

## Fig. x6 Classification Tree
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5}

@@

@@

  resistBetterMix_ASeq <- repMix(resistBetterMix_ASeq)

  treeInput <- rbind( treeInput, resistBetterMix_ASeq )

@@

  #just doing for one strategy, sensiAnPpaer1All.Rmd does for a bunch
  treeResponse <- rownames(resistBetterMix_ASeq)[2] #2 is 25%

  tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
  #treePruned <- prune(tree, cp=tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"])

  #http://stackoverflow.com/questions/29197213/what-is-the-difference-between-rel-error-and-x-error-in-a-rpart-decision-tree
  #A rule of thumb is to choose the lowest level where the rel_error + xstd < xerror.

@@

  #adds in no. scenarios correctly and incorrectly classified
  #prp(tree, extra=1, varlen = 10, main=treeResponse)
  #prp(treePruned, extra=1, varlen = 10, main=treeResponse, col=cols, border.col=cols)
  #prp(treePruned, extra=1, varlen = 0, main=treeResponse, col=cols, border.col=cols)
  prp(treePruned, extra=1, varlen = 0, main='', box.col=cols, under=TRUE)

>>>>

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.
1. Effectiveness of the insecticides is the one input that can change the average relative positioning of the strategies a) sequential and b) adaptive mixture. Below an effectiveness of ~0.55 to 0.6 sequential takes longer to reach the resistance threshold, and above this the adaptive mixture takes longer. 
1. Exposure and effectiveness come out as the most important effect on the difference between the sequential and adpative mixture strategies.
1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.
1. The implication of additional operational costs of adaptive mixtures can be investigated. If a requirement of a 20% improvement in resistance is imposed then more runs favour sequential than mixture.

@@

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='red')
           )       
```

Grey triangles are those runs in which resistance reached the threshold at the same time in the two strategies (and are repeated in both panels). The grey line is a linear model through these same points.

## Fig. x6 Modifying the previous plot to show where resistance arises over 20% slower in an adaptive mixture strategy versus sequential.

1. The line fitted to runs where resistance is reached at the same time for mixture and sequential is retained. Less of the parameter space favours the adaptive mixture under these constraints.

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_diff))+

             facet_grid( ~ mixA_not20pc_better_seq0.25, labeller=as_labeller( c('0'='adaptive mix\nresistance >20% slower','1'='adaptive mix\nresistance <20% slower'))) +

             theme_bw() +
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points abs_diff
             geom_smooth(data=df_same, method = "lm", se = FALSE) 
           )
```

## Fig. x7 Classification Trees for whether resistance arises slower with an adaptive mixture or sequential strategy. The upper plot shows when mixture is slower than sequential, the lower plot is for when the mixture is more than 20% slower.

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5}

@@

  #20% better
  resistBetterMix_ASeqBoolean20 <- resistPointsMix_A > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix_ASeq20 <- plyr::aaply(resistBetterMix_ASeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_ASeq20) <- gsub('gen','betterMix_ASeq20', rownames(resistBetterMix_ASeq20))

@@

  resistBetterMix_ASeq <- repMix(resistBetterMix_ASeq)
  resistBetterMix_ASeq20 <- repMix(resistBetterMix_ASeq20)

  treeInput <- rbind( treeInput, resistBetterMix_ASeq, resistBetterMix_ASeq20 )

@@

  #just doing for a few strategies, sensiAnPpaer1All.Rmd does for a bunch
  treeResponses <- c( rownames(resistBetterMix_ASeq)[2], #2 is 25%
                      rownames(resistBetterMix_ASeq20)[2]
                    )

  #to do trees & plots for all response variables
  for( treeResponse in treeResponses )
  {
    tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
    #http://stackoverflow.com/questions/29197213/what-is-the-difference-between-rel-error-and-x-error-in-a-rpart-decision-tree
    #A rule of thumb is to choose the lowest level where the rel_error + xstd < xerror.

@@

    #adds in no. scenarios correctly and incorrectly classified
    #prp(tree, extra=1, varlen = 10, main=treeResponse)
    #prp(treePruned, extra=1, varlen = 10, main=treeResponse, col=cols, border.col=cols)
    #prp(treePruned, extra=1, varlen = 0, main=treeResponse, box.col=cols, under=TRUE)
    prp(treePruned, extra=1, varlen = 0, main='', box.col=cols, under=TRUE)
    }

### 2016-03-09 resistanceModelNotesAndy.Rmd
figures

@@

~ improve classification tree heading
~ add classification tree for >20% better

>>>>

** 9/3/2016 **

~ creating 20% tree & plot
~ got the 0 line onto the first facet of the 20% plot

@@

reread Curtis to check the below ...

From Ian
~ I think the Curtis result (the one that said sequential was better) assumed effectiveness of both =1 and that exposure =0.9. I think that fits right at the top RH corner of the figure.
